Behavior Driven Development in Haskell

### 2012-06-19 paper.tex
Remove Show instance of Small
It is not required.
BCP: get rid of a usage of we
we use `we' all the time, so one time less won't hurt
Remove Show instance for Small in appendix
typo fix.

As we discussed in Section~\ref{sec:introduction},
We think that some evidence is useful as user documentation.
But there is also evidence, that is not
useful as user documentation.  E.g. that a particular \texttt{Monoid}
instance is a monoid in the mathematical sense is self-evident.

@@

\noindent Where \verb|shouldReturn| has the following type:

@@

\begin{quote}
\small
\begin{verbatim}
newtype Small = Small Int
  deriving Show

@@

\noindent This spec fails when we run it:

@@

-- small non-negative numbers
newtype Small = Small Int
  deriving Show

>>>>

As we discussed in Section~\ref{sec:introduction},
we think that some evidence is useful as user documentation.
But there is also evidence, that is not
useful as user documentation.  E.g. that a particular \texttt{Monoid}
instance is a monoid in the mathematical sense is self-evident.

@@

\noindent where \verb|shouldReturn| has the following type:

@@

\begin{quote}
\small
\begin{verbatim}
newtype Small = Small Int

@@

\noindent This spec fails when run:

@@

-- small non-negative numbers
newtype Small = Small Int
